---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE, error = FALSE
)
```
   
   
# miRTarget : Integrative analysis of miRNA and mRNA
       
     
miRTarget helps to find miRNA predicted and validated targets.  Two databases are used [miRecords](http://c1.accurascience.com/miRecords/) and [miRTarBase](http://mirtarbase.mbc.nctu.edu.tw)
     
     
     
## Installation and loading
    

   
-  Install the latest version from [GitHub](https://github.com/kassambara/miRTarget) as follow: 
    
   
```{r, eval = FALSE}
# Install
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/miRTarget")
```
     
     
- Loading
   
```{r}
library(miRTarget)
```

    
    
## Examples of miRNAs
     
```{r}
miRNAs <- c("hsa-miR-28-5p", "hsa-miR-768-5p")
```
    
    
## Find miRNA targets

    
     
### Get predicted miRNA targets
   
[miRecords.v4](c1.accurascience.com/miRecords/) database is used. For each miRNA, we want to identify the predicted target genes by at least 5/11 databases.
   
The 11 databases are : "diana", "microinspector",	"miranda",	"mirtarget2", "mitarget", "nbmirtar",	"pictar", "pita",	"rna22", "rnahybrid", "targetscan".  
   
    
Internet connexion is required. 
     
     
```{r}
p_targets <- get_mirecords_pt(miRNAs, n = 5, species = "Homo sapiens",
                                      result_file = "mirna_mirecords_predicted_targets.txt")
head(p_targets, 10)
```
    
    
### Get miRNA validated targets
   
   
miRecords and miRtarbase are used. Internet connexion is required.
    
    
1. miRecords
    
    
```{r}
mirecords_vt <- get_mirecords_vt(miRNAs, 
                                 species = "Homo sapiens", version = 4)
head(mirecords_vt, 10)
```
    
    
2. miRtarbase
     
     
```{r}
mirtarbase_vt <- get_mirtarbase_vt(miRNAs)
head(mirtarbase_vt, 10)
```
    
    
3. Combine validated targets
    
    
```{r}
v_targets <- combine_mir_vt(mirecords_vt, mirtarbase_vt)
# head(v_targets) 
```
    
    
### Merge predicted and validated targets   
     
     
```{r}
targets <- combine_mir_pvt(p_targets, v_targets)
head(targets)
```
    
     
